### 2017-10-08 TF-vldb2018/full/sec-appendix.tex

The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
(a) $\max_i |P_{fi}| \leq r_1\cdot\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.

@@

\revise{
\vspace{-1.5ex}
\etitle{Lower bound.}
We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.

\vspace{-1ex}
An instance of the minimum cut problem is given an undirected graph $H=(V_{H},E_{H})$ and a positive integer $m$,
to find a set $S \subseteq E_{H}$ of edges whose removal leaves two disjoint connected components, with $|S|\leq m$.

\vspace{-1ex}
Given an instance of the minimum cut problem,
we construct an instance of $h$-fragmentation problem.
It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.}

\eat{%%%% Wrong proof %%%
\vspace{-2.5ex}
\etitle{Lower bound.}
We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.

\vspace{-2ex}
An instance of the minimum cut problem is given an undirected graph $H=(V_{H},E_{H})$ and a positive integer $m$,
to find a set $S \subseteq E_{H}$ of edges whose removal leaves two disjoint connected components, with $|S|\leq m$.

\vspace{-2ex}
Given an instance of the minimum cut problem,
we construct an instance of $h$-fragmentation problem.
It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.
}%%EAT

@@

\vspace{1ex}
\noindent
{\large \textbf{Appendix D: Extra Experiments}}
\label{sec-apd-exp}

>>>>

The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
(a) $\max_i |P_{fi}| \leq r_1\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.

@@

\vspace{-1.5ex}
\etitle{Lower bound}.
We next show that $\kw{dOFGP}(P, h, r_1, r_2)$ is \NP-hard by
reduction from the 3\SAT\ problem. An instance of 3\SAT\ is a formula
$\psi = C_{1}\land \ldots \land C_{m}$, where each $C_{i}$ is a
disjunction of three literals, \ie $C_{i} = \ell_{1}^{i}\lor
\ell^{i}_{2}\lor \ell^{i}_{3} (i\in [1, m])$, in which
$\ell_{j}^{i}(j\in [1, 3])$ is either a variable $x_{k}$ or the
negation of variable $\bar x_{k} (k\in [1, n])$ from a universal set $U =
\{x_{1}, \ldots, x_{n}\}$ of variables. Given a $\psi$, 3\SAT\ is to decide
whether $\psi$ is satisfiable, \ie there exists a truth assignment $\mu$ to
variables in $U$ such that $\psi$ is \True\ under $\mu$. It is known that 3\SAT\
is \NP-complete~\cite{Papa1994}.

\vspace{-1.5ex}
Given $\psi$ of 3\SAT, we next construct an instance of $\kw{dOFGP}$, \ie a
pattern graph $P$, the number of fragments $h$, and two ratios $r_{1}$ and
$r_{2}$, such that $\psi$ is satisfiable if and only if $\kw{dOFGP}(P, h,
r_{1}, r_{2})$ is \True.

\vspace{-1.5ex}
\eetitle{(1) Pattern graph $P$}. Pattern $P$ is constructed in two steps:
(1.a) construct a graph $P'$; and (1.b) expand $P'$ to $P$. We below
describe the two steps.

\vspace{-1.5ex}
\sstab
(1.a) $P'$ is constructed as follows. 
First, for each $C_{i} (i\in [1, m])$, construct a set $V_{i}$ of
three nodes $u_{1}^{i}$, $u_{2}^{i}$, and $u_{3}^{i}$, yielding $3m$ nodes in
$V_{1}$, \ldots, $V_{m}$. Intuitively, node $u^{i}_{j}(i\in [1, m], j\in
[1, 3])$ is to encode literal $\ell_{j}^{i}$. 
Then connect nodes as follows: for each $i, j \in [1, m]$ and $i\neq j$, connect
$u^{i}_{s}$ in $V_{i}$ and $u^{j}_{t}$ in $V_{j}$ ($s, t\in [1, 3]$) if they do not encode
complement literals, \ie $\ell^{j}_{t} \neq \bar \ell^{i}_{s}$. In other words,
$u^{j}_{t}$ and $u^{i}_{s}$ are not connected only when $\ell^{i}_{s} = x$ and
$\ell^{j}_{t} = \bar x$ or $\ell^{i}_{s} = \bar x$ and
$\ell^{j}_{t} = x$  for some $x \in U$.

%One can verify the following property.

%Property (I): $\psi$ is satisfiable if and only if $P'$ has an $m$-clique.

\vspace{-1.5ex}
\sstab
(1.b) We next expand $P'$ to $P$ as follows. For each node set $V_{i}$
constructed in $P'$, connect it with an $(m-2)$-clique $K_{i}$, such that 
each node $u^{i}_{j}(j\in [1,3])$ in $V_{i}$ is connected to every node in
the clique $K_{i}$.

%Hence $P$ has $(m-2) * m + 3m = m^{2}+m$ nodes and $(C_{m-2}^{2}+3*(m-2))*m + $
%One can verify the following property.

%Property (II): $P$ has

\vspace{-1.5ex}
\eetitle{(2) $h$}.  Let $h = m + 1$.

\vspace{-2ex}
\eetitle{(3) $r_{1}$}. Let $r_{1} = (m+1)*(C_{m}^{2}+m)/|P|$, \ie
$r_{1}*\dfrac{|P|}{h} = C_{m}^{2}+m$ is the size of a $m$-clique.

\vspace{-1.5ex}
\eetitle{(4) $r_{2}$}. Let $r_{2} = \dfrac{|E_{P}| - (C_{m}^{2} + m) -
	m*(C_{m}^{2} + m -1)}{|P|}$.

\vspace{-1.0ex}
One can verify that $\psi$ is satisfiable if and only if $P$ has an $h$-fragmentation $P_{1}$,
\ldots, $P_{h}$ such that $max_{i}|P_{i}|\leq r_{1}*\frac{|P|}{h} (i\in [1, h])$
and $|C|\leq r_{2}*|P|$.
This indeed is verified by using the following properties of
the above construction:

\vspace{-2.5ex}
\bi
\item[$\circ$] $\psi$ is satisfiable if and only if $P'$ has an $m$-clique; 
\item[$\circ$] $P$ has a unique $m+1$ fragmentation satisfying that
(i) an $m$-clique is the largest fragment and
(ii) cut is no larger than $|E_{P}| - (C_{m}^{2} + m) -
m*(C_{m}^{2} + m -1)$: the $m$-clique fragment must come from $P'$, which
leaves the $m$ extended $(m-2)$-clique as the remaining $m$ fragments, each
of size equal to that of an $m$-clique minus 1.
\ei

@@

\noindent
{\large \textbf{Appendix D: Extra Experiments}}
\label{sec-apd-exp}
